### 2022-02-22 draft2.tex
sample distributions reworked

For a forecast represented as a parametric function with pmf/pdf $p_m(x)$, 
the accuracy of the forecast may be measured as how likely realized value $x^*$
is to occur. Commonly used proper scoring rules for parametric distributions
include the Logarithmic score (LogS), 
continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
\cite{alves2013ncep} and the interval/Brier 
score \cite{gneiting2007strictly} among 
others. See also \cite{gneiting2014probabilistic}
section 3 for on proper scoring functions. Unless otherwise noted, the following
definitions/reviews can be found in the review by Krueger.

@@

\begin{equation}
  LS(p_m,x*) = -log\;p_m(x^*)
\end{equation}

\subsection{Forecast as samples}
A random sample $(X_1,...,X_n)$ where $X_i \sim D$ may be used to 
estimate values such as the mean or quantiles of the distribution $D$.

According to the Strong Law of Large numbers, the sample mean will converge to
the expected value of distribution as $n$ approaches $\infty$ as long as the 
expected value of that distribution exists. Likewise by the same law the 
empirical distribution function will converge to the true cumulative 
distribution function as $n$ approches $\infty$. Thus, if a sufficiently large 
sample is generated from a distribution, the sample will closely approximate the 
true distribution.

@@

In the last few decades, increased computing power and improvements in MCMC
sampling have greatly contributed to growth in the use of
predictive distributions \cite{gneiting2007strictly}.

@@

For a forecast of drawn samples, the ECDF may be computed and the CRPS used to 
score the prediction. The CRPS has some nice properties, but can sometimes be
difficult to compute. For example, when the forecast is a mixture of a 
Truncated Normal distribution (TN) and a Truncated Lognormal (TL) the CRPS is 
not available in closed form \cite{baran2018combining}.

@@

Considered the state-of-the-art techniques for combining component distributions
into a multi-model ensemble are nonhomogeneous regression (NR), also known as
ensemble model output statistics (EMOS), and ensemble Bayesian model averaging
(BMA), both of which will be defined as in \cite{gneiting2014probabilistic}.

\begin{equation}
  p^E(y) = \sum_{j=1}^J w_jp_j(y)
\end{equation}
where $p_j$ is the $j^{th}$ component forecast distribution and 
$0 \leq w_j \leq 1$ is a weight assigned to each component where $\sum w_j = 1$.
Methods for estimating weights include Maximum Likelihood estimation
\cite{raftery2005using}, MCMC 
sampling see \cite{vrugt2008ensemble} (also in this paper it talks about how 
EM can get difficult as parameters i.e. number of distributions increase, and 
shows MCMC may be better with that high dimensionality and gives full posterior
of weights)
and minimizing CRPS as in 
\cite{baran2018combining}.

@@

\begin{table}[h!]
\centering
 \begin{tabular}{||c c c c||} 
 \hline
 Family & param1 & param2 & param3 \\ [0.5ex] 
 \hline\hline
 lnorm & 1 & 0.4 & NA \\ 
 \hline
 \end{tabular}
\end{table}

>>>>

% \subsubsubsection{Scoring}
For a forecast represented as a parametric function with pmf/pdf $p_m(x)$, 
the accuracy of the forecast may be measured as how likely realized value $x^*$
is to occur. Commonly used proper scoring rules for parametric distributions
include the Logarithmic score (LogS), 
continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
\cite{alves2013ncep} and the interval/Brier 
score \cite{gneiting2007strictly} among 
others. See also \cite{gneiting2014probabilistic}
section 3 for on proper scoring functions. Unless otherwise noted, the following
definitions/reviews can be found in the review by Krueger.

@@

\begin{equation}
  LS(p_m,x*) = -log\;p_m(x^*)
\end{equation}
The goal is to minimize the LogS, so that a forecast $p{'}_m(x^*)$ is deemed 
superior to $p_m$ if
$LS(p{'}_m, x^*) < LS(p_m, x^*)$.
The LogS is strictly limited to scoring forecasts with density functions and
evaluating those densities only at the point $x^*$.

The CRPS is a function of a CDF $F$
and so 
can be used a bit more extensively than the LogS which is limited to 
distributions which carry a density. For the CDF $F_m$, the CRPS is defined as

\begin{equation}
\label{eq:crps}
  CRPS(F_m, x^*) = \int_{-\infty}^{\infty} (F_m(x)- 1_{\{x*\leq x\}})^2 dy
\end{equation}
Here too a smaller score indicates a better forecast.

Besides evaluating forecasts, the CRPS is also used in optimizing weights used
to build ensembles. Considered the state-of-the-art techniques for combining 
component distributions
into a multi-model ensemble are nonhomogeneous regression (NR), also known as
ensemble model output statistics (EMOS), and ensemble Bayesian model averaging
(BMA), both of which will be defined as in \cite{gneiting2014probabilistic}.

\begin{equation}
  p^E(x) = \sum_{jm=1}^M w_mp_m(x)
\end{equation}
where $p_m$ is the $j^{th}$ component forecast distribution and 
$0 \leq w_m \leq 1$ is a weight assigned to each component where $\sum w_m = 1$.
Methods for estimating weights include Maximum Likelihood estimation
\cite{raftery2005using}, MCMC 
sampling see \cite{vrugt2008ensemble} (also in this paper it talks about how 
EM can get difficult as parameters i.e. number of distributions increase, and 
shows MCMC may be better with that high dimensionality and gives full posterior
of weights)
and minimizing the CRPS as in 
\cite{baran2018combining}.

For selecting distribution weights, the CRPS has some nice properties, but can 
sometimes be
difficult to compute. For example, when the forecast is a mixture of a 
Truncated Normal distribution (TN) and a Truncated Lognormal (TL) the CRPS is 
not available in closed form \cite{baran2018combining}.

Generally computation and evaluation of parametric distributions is not hard. 
For most commonly used parametric distributions -Normal, Lognorm, Poisson,
Gamma, etc.- there is software readily available to compute density, 
distribution and quantile values. Likewise, requirements for storage are low 
compared to other uncertainty representations we will discuss. The most common
parametric distributions can be fully defined with three or pieces of data.
The distribution family and two or three parameters. Below shows a table with
enough information to completely define a $Lognormal(1,0.4)$ distribution.

\begin{table}[h!]
\centering
 \begin{tabular}{|c c c|} 
 \hline
 Family & param1 & param2 \\ [0.5ex] 
 \hline
 lnorm & 1 & 0.4 \\ 
 \hline
 \end{tabular}
\end{table}

A completely defined continuous parametric distribution can be evaluated at an
infinite number of values. We will call this an infinite resolution.

A drawback of representing a forecast in a parametric distribution is the lack 
of flexibility in the model selection. Easy computation and evaluation of these 
models is limited to what is available in software, so certain distributional
shapes may unattainable. The distribution may assign probability to values
outside the range of the forecast. There are remedies for this such as 
truncation, but these increase the complexity in evaluation and scoring.
Requiring a parametric forecast also bars the use of some statistical methods
which might be used to create a forecast model including some Bayesian methods
where a posterior distribution cannot be computed in closed form.

\subsubsection{Sample Distributions}
Some forecast model builders may want more flexibility than a parametric 
distribution can provide. Some methods such as sampling from a posterior 
distribution or resampling methods like Bootstrap will produce forecasts of
sample distributions.

A sample distribution is built of a sample of random variables 
$(X_1,...,X_n)$ where $X_i \sim D$ and $D$ is a distribution. From this, sample
statistics such as mean, median, variance and quantiles may be calculated. 
An empirical cumulative distribution function (ECDF) may also be calculated as

\begin{equation}
\label{eq:ecdf}
  F_n(x) = \frac{1}{n} \sum_{i=1}^n \mathbb{I}(X_i \leq x)
\end{equation}

According to the Strong Law of Large numbers, the sample mean will converge to
the expected value of distribution as $n \rightarrow \infty$ as long as the 
expected value of that distribution exists. Likewise by the same law the 
ECDF will converge to the true CDF 
distribution function as $n \rightarrow \infty$. Thus, if a sufficiently large 
sample is generated from a distribution, the sample will closely approximate the 
true distribution.

@@

In the last few decades, increased computing power and improvements in MCMC
sampling have greatly contributed to growth in the use of
predictive distributions \cite{gneiting2007strictly}. (See examples listed in
\cite{krueger2016probabilistic}).

To properly score a forecast represented by a sample distribution, both the CRPS
and LogS may be used. The CRPS has the advantage here of scoring the sample 
distribution directly since the CDF in  (\ref{eq:crps}) may be replaced by 
(\ref{eq:ecdf}). To use the LogS to score a forecast, a density function for the 
sample must be approximated. Common approximations include a kernel density (KD)
or Gaussian approximation (GA).

KD is defined in Kruger as

\begin{equation}
\label{eq:kd}
  \hat{p}_n(x) = \frac{1}{n h_n} \sum_{i=1}^n K \left( \frac{x-X_i}{h_n} \right) 
\end{equation}
where $K$ is a kernel function, and $h_n$ is a bandwidth

Kruger et. al compare scoring of MCMC drawn forecast distributions using CRPS 
and LogS over samples directly using ECDF or over density approximations using
KD or GA.

@@

For a forecast of drawn samples, the ECDF may be computed and the CRPS used to 
score the prediction.

@@

@@
